R Tools for Obspack, Footprints and Receptors (rtorf)

### 2024-07-08 README.Rmd
docs

 <!-- badges: start -->

![GitHub commit
activity](https://img.shields.io/github/commit-activity/y/noaa-gml/rtorf)
  [![R-CMD-check](https://github.com/noaa-gml/rtorf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/noaa-gml/rtorf/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->

>>>>

![GitHub commit activity](https://img.shields.io/github/commit-activity/y/noaa-gml/rtorf)
[![R-CMD-check](https://github.com/noaa-gml/rtorf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/noaa-gml/rtorf/actions/workflows/R-CMD-check.yaml)
![GitHub Repo stars](https://img.shields.io/github/stars/noaa-gml/rtorf)
